### 2022-08-10 ms/ms02_floats.tex
ENH cytoband

% full size table is table*
\begin{table*}[]
  \caption{Variants involved in 5 or more GWAS categories.}\label{tab:pleitropic_variants}
\centering
\scriptsize
\hline
\csvreader[separator=tab,
tabular=rrrcp{0.6\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Pos. (hg38) & \bfseries Variant & \bfseries Cat. ct. & \bfseries GWAS Categories\\\hline,
]{fig/tab_rsid_most_pleiotropic.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv & \csvcolv}% specify your coloumns here
\hline
\end{table*}

@@

% full size table is table*
\begin{table*}[]
\caption{Pleiotropic regions involving 6 or more GWAS categories.}\label{tab:pleiotropic_regions}
\centering
\scriptsize
\hline
\csvreader[
separator=tab,
tabular=rrrcp{0.5\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Start (hg38) & \bfseries End (hg38) & \bfseries Cat. ct. & \bfseries GWAS Categories\\\hline,
]{fig/tab_region_window_100000_pleio_highest.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv & \csvcolv}% specify your coloumns here
\hline
\end{table*}

>>>>

% full size table is table*
\begin{table*}[]
  \caption{Variants involved in 5 or more GWAS categories.}\label{tab:pleitropic_variants}
\centering
\scriptsize
\hline
\csvreader[separator=tab,
tabular=rrrrcp{0.6\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Cytoband & \bfseries Pos. (hg38) & \bfseries Variant & \bfseries Cat. ct. & \bfseries GWAS Categories\\\hline,
]{fig/tab_rsid_most_pleiotropic.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv & \csvcolv & \csvcolvi}% specify your coloumns here
\hline
\end{table*}

% full size table is table*
\begin{table*}[]
\caption{Pleiotropic regions involving 6 or more GWAS categories.}\label{tab:pleiotropic_regions}
\centering
\scriptsize
\hline
\csvreader[
separator=tab,
tabular=rrrrcp{0.5\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Cytoband & \bfseries Start (hg38) & \bfseries End (hg38) & \bfseries Cat. ct. & \bfseries GWAS Categories\\\hline,
]{fig/tab_region_window_100000_pleio_highest.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv & \csvcolv & \csvcolvi}% specify your coloumns here
\hline
\end{table*}

@@
